
%%--------------------------------%%
\begin{frame}
    \frametitle{1988 Viability Assessment}

    The 1988 \textbf{Viability Assessment} describes the nuclear waste problem and 
    explains why the United States and other nations are considering deep 
    geologic disposal as the solution. It also describes what research must be 
    done to complete a license application.

    \textbf{Public hearings} are held about this viability assessment and with this, the 
    Yucca Mountain site was deemed a viable site for further characterization 
    and the \textbf{pursuit of a license application} began. 

  \end{frame}

\begin{frame}
    \frametitle{1991-2002 Site Characterization}
    The process of researching the suitability of Yucca Mountain began 
    \begin{itemize}
      \item 1991 - surface studies begin 
      \item 1999 - bills for interim storage at the Nevada Test Site are 
        introduced. Bill Clinton vows to veto them.
      \item 2000 - The environmental impact statement is release for public 
        comment.
      \item 2001 - EPA proposes radiation standards for Yucca Mountain. The 
        State of Nevada files suit against the EPA concerning the standards.
    \end{itemize}
  \end{frame}

%%--------------------------------%%
\begin{frame}
\frametitle{Nuclear Waste Fund Litigation}
    \begin{itemize}
    \item 1983 - Nuclear utilities signed the Standard Contract agreeing to pay the nuclear waste fee.
    \item 1998 - The utilities sue the federal government over the delay in used fuel acceptance.
    \item 1998 - Courts ruled the DOE is partially liable. DOE settled. 
    \item DOE developed an amended Standard Contract \cite{doe_standard_????} to 
      address new reactors.
  \end{itemize}
\end{frame}

%%--------------------------------%%
\begin{frame}
    \frametitle{2002 - 2008 Site Recommendation}
    \begin{itemize}
      \item 2002- The site was deemed appropriately characterized for recommendation in 2002.  \textbf{Secretary of Energy}$\longrightarrow$\textbf{President 
      Bush}$\longrightarrow$\textbf{Congress}
     \item 2004 - In the Nevada Lawsuit, the EPA 10,000 year radiation standard 
       is deemed inadequate. The rest of the radiation standards remain. 
   \end{itemize}
  \end{frame}

%%--------------------------------%%
\begin{frame}
    \frametitle{2008 - 2013 License Application and Withdrawal}
    \begin{itemize}
      \item The license application was \textbf{submitted} to the NRC in 2008.
      \item The NRC was expected to make a decision \textbf{within 4 years}.
      \item In \textbf{May 2009}, Secretary Steven Chu stated: ``Yucca Mountain as a 
        repository is off the table''.
      \item \textbf{July 2009}, the House of Representatives voted 388 to 30 to 
        not defund the Yucca Mountain repository in the FY2010 budget.
      \item On \textbf{March 3, 2010}, the DOE filed a motion with the NRC to 
        withdraw its license application. 
      \item \textbf{Lawsuits} erupted from Hanford, WA and Aiken County, SC, among 
        others.
      \item YMP funding was terminated with the Defense and Full-Year Continuing 
        Appropriations Act, passed by Congress on \textbf{April 14, 2011}.
    \end{itemize}
  \end{frame}



